Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-11-15 paper/paper.tex
Minor changes to paper

Competition, in the context of this model, is a repulsive effect which acts
between any two branches, whether they originate from different retinal
ganglion cells or from the same cell. It assumes that there is some kind of
self-other signal (\textbf{be sure to discuss possible origins}) which acts to
discourage two cells from approaching each other.
%
\begin{equation}
\mathbf{C}_b = \frac{1}{|B_{b,c}|} \sum_k \hat{\mathbf{x}}_{kb} W
\end{equation}
where the distance based weight $W$ is given by
\begin{equation}
W(d_{kb}) = \begin{cases}
      1 - \frac{d_{kb}}{2r}   & d_{kb} \leq 2r_c \\
     0 & d_{kb} > 2r_c
     \end{cases}
\end{equation}
for two growth cones of interaction radius $r_c$ separated by a distance
$d_{kb}$. $B_{b,c}$ is the set of growth cones within a distance $2r_c$ of
branch $b$.

@@

We model interactions between axon growth cones due to signalling between
receptors of the same type. For these interactions, repulsion causes a
movement of branch $b$ along a unit vector, $\hat{\mathbf{x}}_{kb}$, from
branch $k$ to branch $b$ causing them to move further apart; attraction causes
the opposite movement. The interaction, $\mathbf{I}_b$, acting on branch $b$,
is given by

\textbf{FIXME} In the code, I'm mostly using the Reber-like ratio based
interaction, as described in Simpson and Goodhill.

%
\begin{equation}
% No \frac{1}{|B_b|} in this one. Really?
\mathbf{I}_b = \sum_k \hat{\mathbf{x}}_{kb}\,Q(d_{kb})
\end{equation}
%
where $Q_I(d_{kb})$ is the signalling strength between two growth cones of
receptor-receptor interaction radius $r_i$ a distance $d_{kb}$ from one
another, given by
%
\begin{equation}
Q_I(d_{kb}) = \begin{cases}
     \sum_i^N E_i\,r_{i,b}\,r_{i,k}    & d_{kb} \leq 2r_i \\
     0 & d_{kb} > 2r_i
     \end{cases}
\end{equation}
%
The sign of $Q_I$ is dependent on the values of $E_i$, which determines
whether the receptor-recetpro interaction, $\mathbf{I}_b$, is repulsive or
attractive. $r_{i,k}$ is the expression of receptor $i$ on branch $k$.

>>>>

Competition, in the context of this model, is a repulsive effect which acts
between any two branches, whether they originate from different retinal
ganglion cells or from the same cell. It assumes that there is some kind of
self-other signal (\textbf{be sure to discuss possible origins}) which acts to
discourage two cells from approaching each other.
%
\begin{equation}
\mathbf{C}_b = \frac{1}{|B_{b,c}|} \sum_k \hat{\mathbf{x}}_{kb} W
\end{equation}
where the distance based weight $W$ is given by
\begin{equation}
W_c(d_{kb}) = \begin{cases}
      1 - \frac{d_{kb}}{2r_c}   & d_{kb} \leq 2r_c \\
     0 & d_{kb} > 2r_c
     \end{cases}
\end{equation}
for two growth cones of interaction radius $r_c$ separated by a distance
$d_{kb}$. $B_{b,c}$ is the set of growth cones within a distance $2r_c$ of
branch $b$.

@@

We model interactions between axon growth cones due to signalling between
receptors of the same type. For these interactions, repulsion causes a
movement of branch $b$ along a unit vector, $\hat{\mathbf{x}}_{kb}$, from
branch $k$ to branch $b$ causing them to move further apart; attraction causes
the opposite movement. The interaction, $\mathbf{I}_b$, acting on branch $b$,
is given by
%
\begin{equation}
% No \frac{1}{|B_b|} in this one. Really?
\mathbf{I}_b
= \frac{1}{|B_{b,I}|} \sum_k \sum_i \hat{\mathbf{x}}_{kb}\,W_I \qquad \mathrm{if}~r_{i,b}
/ r_{i,k} < 1.1
\end{equation}
%
the weight here is defined as a function of $r_I$:
%
\begin{equation}
W_I(d_{kb}) = \begin{cases}
      1 - \frac{d_{kb}}{2r_I}   & d_{kb} \leq 2r_I \\
     0 & d_{kb} > 2r_I
     \end{cases}
\end{equation}
$r_{i,k}$ is the expression of receptor $i$ on branch $k$.
